	\documentclass[a4paper,12 pt,openany]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{xltabular}
\usepackage[a4paper]{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2.5cm,lmargin=1.5cm,rmargin=2cm}
%\usepackage[absolute,overlay]{textpos}
\usepackage[absolute,overlay,showboxes]{textpos}
%\usepackage[width=457.86mm, height=303.28mm]{geometry}
\pagenumbering{gobble}

\newcommand{\linex}{\rule{\textwidth}{0.4pt}}

\begin{document}


\center

\footnotesize

\begin{textblock*}{19 cm}(1cm,1cm) % box width, coord X, coord Y
\flushleft

\begin{multicols}{2}

\textbf{Blind}:\index{Blind} The character can't see anything. -2 Skills based on Strength and Dexterity. Trials or tasks based on vision automatically fail. All opponents are treated as having invisibility towards the blinded character. Attacking a creature invisible to it has a -1d6 attack roll, an invisible creature attacking a blind creature has a +1d6 attack roll.

\textbf{Charmed}:\index{Charmed}: A charmed creature cannot attack or target the charmer. Any new saving throw threat, if a clear and concrete threat automatically interrupts the effect. An ally of the charmed creature can shake it to allow it to make a new saving throw by spending 2 Actions. The charmer has +1d6 on any ability checks to interact socially with the creature.

\textbf{Grabbed}\index{Grabbed}: A grabbed character cannot move but can try to Push. He must use two Actions to free himself (ST Fortitude opposed by Strength + 1d6 by Size). He can attack with melee weapons if appropriate. -2 to Hit Rolls.

\textbf{Drown/Hold breath}: \index{Drown}\index{Hold breath} Hold breath equal to 6 rounds per Constitution, minimum 3 rounds. For each Action performed -1 round to . Feint air On a DC 12 Fortitude save each round to continue holding the breath. Each round, DC increases by 1.

\textbf{Deafened}:\index{Deafened}\index{Deaf} Automatically fails all sound-based Awareness checks and is considered Distracted when casting spells that have verbal components.

\textbf{Blocked}\index{Blocked}: A blocked creature has its arms blocked. He can move trying to Push, he must use two Actions to free himself (ST Fortitude opposed). He loses his Dexterity bonus on Defense and Reflex saves. A blocked spellcaster must make a critically successful Spell Check or fail to cast spells. -1d6 to hit rools.

\textbf{Confused}: \index{Confused}

\textbf{d100 Behavior:}

01-25 Acts normally

26-50 All he does is stammer incoherently

51-75 Deals 1d8 + Strength to self with weapon in hand

76-100 Attacks closest creature (for this purpose, a Familiar counts as part of the subject itself)

Any confused creature that is attacked automatically attacks its attacker again on its next round.

\textbf{Fatigued}\index{Fatigued}: Cannot run or charge and takes a -2 penalty on attack rolls, defense, and saving throws.
If he does anything normally tiring, his Fatigued rating increases and he also takes penalties on movement and proficiency checks.

\medskip

\begin{tabularx}{0.45\textwidth}{lcl}
	\textbf{Conditions}& \textbf{Pen./Mov/Prof.}&\textbf{Rec.}\\
	\hline
	Fatigued &2/-/-&1h\\
	Fatigued 2&4/2m/-4&1h\\
	Fatigued 3&6/3m/-6&8h\\
	Fatigued 4&8/6m/-8&12h\\
	Fatigued 5&Stunned&12h\\
	Fatigued 6&Death&--\\
\end{tabularx}


\textbf{Flat-footed/Surprised}\index{Flat-footed}: a flat-footed creature has -4 to Defence and Reflex Saving Throw. Cannot use Actions or Reactions unless explicitly permitted.

\textbf{Incapacitated}\index{Incapacitated}: An incapacitated creature cannot take actions or reactions. Melee attacks against an incapacitated creature have a +1d6 bonus. She's Flat-footed (-4 Defence and Reflex Saving Throw).

\textbf{Helpless}:\index{Helpless} A character asleep, unconscious, dying, or for some other reason completely at the mercy of his opponents is considered helpless.
A helpless creature cannot take Actions or Reactions or speak, attacks against it have a +2d6 bonus. He is unaware of what is happening around him. The creature drops anything it is holding and falls prone.
The creature automatically fails Fortitude and Reflex saves.

\textbf{Entangled}:\index{Entangled} An entangled creature treats terrain as difficult, cannot Run or Charge, -2 penalty on Defense, attack rolls and his distracted.


\textbf{Paralysed}: \index{Paralysed} Paralyzed character is frozen in place and unable to move or act, he is \textbf{Helpless} and can only perform mental actions.

\textbf{Fear, Frightened}:\index{Fear}\index{Feared} A frightened creature has -1d6 on attack rolls, saving throws, and Proficiency Checks as long as the source of its fear is visible. A frightened creature cannot voluntarily approach the source of its fear.

\textbf{Prone}\index{Prone}: whoever is prone has a -1d6 to attack and a -4 to Defense. Getting up from prone costs 2 Actions. You cannot become prone if you fly.

\textbf{Slowed}\index{Slowed}: Slowed down is indicated with two values, the first indicates how many less Actions are done per round, the second the duration of the effect, if marked with a - then it has no indicated end. Ex. Slowed 1/3r, Slowed 2/- 

\textbf{Stunned/Knocked Out}:\index{Stunned}\index{Knocked Out} is considered Helpless. He cannot move.

\textbf{Unprepared / Surprised}\index{Unprepared}\index{Surprised}:
A surprised/flat-footed creature has a -4 penalty to Defense and Reflex saves. No Reactions and Actions for that round.


\end{multicols}

\end{textblock*}


\begin{textblock*}{14cm}(1cm,23.2cm)
\textbf{Reading a Scroll}

\textbf{in case of ISY SCROLL scrolls}: production cost level*level*160gp

- Understand: Intelligence or Arcana DC 10

- Cast: Intelligence or Arcana DC 12.

\textbf{in case of normal scrolls}: production cost level*level*80gp

- Understand: Arcana difficulty 15

- Cast: Arcana DC 20 and have access to the Magic List
\end{textblock*}


~\newpage

\begin{textblock*}{4cm}(1cm,1cm) % box width, coord X, coord Y
{\textbf{Fate Points}\\
(20-Level)/5}

\linex

{\textbf{Death}\\
HP=-10-(COS*2)}

\linex

\textbf{Cover - Defense}
Light +2 (>50\%)\\
Average +4 (<50\%)\\
Complete +8 (5\%)\\
Half to ST Reflex

\linex

\textbf{Power Blows}\\
+1 to damage - 2 CT. MAX CA/4

\linex

\textbf{Combat mastery}\\
+2 Defense -1d6 to Attack Roll\\
-2 Defense +1 Attack Roll \\
No more than +-2d6 can be awarded in this manner.
1 Action = +2 Defense

\linex

\textbf{Upload}\\
3 Actions. +1d6 to attack, -4 to defense, -10 attacks beyond

\linex

\textbf{Attack of opportunity}\\
On the move, it exits or crosses the melee zone. This attack is a Reaction that costs an Action.

\linex

\textbf{Multiple Attacks}\\
The first attack action has no penalty while the second attack action has -5 to cumulative hit per attack

\linex

\textbf{Total defense}\\
2 Actions. No Attack, NO Spells, you can only take one Action and gain +4 in Defense. You do not cause attacks of opportunity if you cross an opponent's melee range.

\linex


\end{textblock*}

\begin{textblock*}{8.3cm}(5.3cm,1cm)

\textbf{Breaking Objects - DC Force}\\
\begin{tabular}{ll|ll}
Rope & 23& Simple Door & 13\\
Wooden door & 15& Strong door & 18\\
Iron Door & 28& Chain & 26 \\
\end{tabular}

\linex

\begin{tabular}{lll}
\textbf{Difficulty} & \textbf{Description} & \textbf{Competence} \\
DC 5 & Extremely Easy & Mediocre \\
DC 10 & Easy & Normal \\
DC 15 & Normal & Good \\
DC 20 & Difficult & Best \\
DC 25 & Very Difficult & Excellent \\
DC 30 & Extremely Hard & Amazing \\
DC 35 & Near Impossible & Legendary \\
DC 40 & Legendary & Beyond Human \\
\end{tabular}


\linex

\textbf{Actions per Round}

\begin{tabular}{ll}
Perform an attack & 1\\
Perform two attacks & 2\\
Perform more than two attacks & 3\\
Cast a Spell* & 2\\
Perform a Move Action* & 1\\
Shot & 1\\
Standing up from prone & 2\\
Help someone & 2\\
Exchange a dialogue with someone* & 3\\
\small{Exchange a few words with someone*} & 0\\
Searching for something in the backpack & 2\\
Use a hand held item & 1\\
{\small Take from belt or ready} & 1\\
Drink a potion held at the belt & 1\\
Drawing/Sheathing Weapon & 1\\
Holding the Shield & 1\\
Using a Magic Item & 2\\
Test a skill* & 1\\
Breaking down a door with shoulder or kicks&1\\
Forcing down a door with a crowbar &2\\
Hide & 1\\
Focus on a Spell & 1\\
Mount or dismount & 1\\
Action \textbf{I}immediate - Action \textbf{R}eaction & I - R\\
Drinking a hand held potion & I\\
Throwing a hand held object & R\\
Fall prone & R\\
Recognize a Spell & R\\
\end{tabular}

\linex

\textbf{Stand up from prone}\\
2 Actions. -4 Defense, -4 Initiative. Acrobatics DC 13 1 Action stand up. Three 1s you lose the round. Acrobatics (6p) 1 Action, Acrobatics (8p) Immediate Action.

\linex

\textbf{Standard Size and Capacity}\\
\begin{tabular}{lll}
\textbf{Size}& \textbf{Space} &\textbf{Range}\\
Small & 25 x 25 cm&0m\\
Small & 0.5 x 0.5m &0m\\
Medium & 1 x 1m & 1m\\
Large & 3 x 3m & 2m\\
Huge & 5 x 5m &3m\\
Mammoth & 6 x 6m&4m\\
Colossal & 12 x 12m&6m\\
\end{tabular}

\linex

\textbf{Vision}\\

A blinded creature \index{Blinded} takes a -1d6 penalty on Awareness checks and a -2 penalty on Strength- and Dexterity-based checks, and automatically fails any sight-dependent Awareness check.

Using Darkvision/Low light vision: Survival check to search for traps or visual-only Awareness takes a -2 penalty.

Fight in dim light cause -2 to Hit Roll.


\end{textblock*}

\begin{textblock*}{6.2cm}(13.8cm,1cm) % box width, coord X, coord Y
\textbf{Mod. to combat}\\
\textbf{Attack}:
\textbf{+2}: flank

\textbf{+1d6}: you are invisible, charge

\textbf{-2}: dazzled, hampered, entangled, dim light

\textbf{-1d6}: prone, shrunk, frightened, shaken, thrown weapons on melee, unknown weapon, inv creature but located, climbing

\textbf{Defense}: +2/4/8: light(30\%)/ medium(50\%)/ full(80\%) coverage

\textbf{-2}: grabbed \textbf{-4}: trapped, kneeling, sitting, prone, constricted, dazed, casting a spell, climbing
\linex

\textbf{Rest 8 hours} \\recovers COS+2xWP+MP HP, minimum 1.

\linex

\textbf{Temporary damage}\\ Every hour you recover, with a minimum of 1 HP, your Constitution value in lost non-lethal HP (damage from stunning).

\linex

\textbf{Surprised Defense}\\ -4 Defense, -4 Reflex save

\linex

\textbf{Touch Attack}\\ +1d6 To Hit

\linex

\textbf{Critical Hit}\\
Each time you hit, you roll one additional weapon die and add no more for every two times you rolled a 6 on the Attack Roll.

\linex

\textbf{Burst Damage}\\
If the die roll is the maximum value (min 8) you take the die back and add up again the value (of the die only).

\linex

\textbf{Get defensive}\\
you use one action, +1 Defense until start of round after.


\linex

\textbf{Attacks with Splash Weapons}\\
1 2 3\\
4 \textbf{X} 5\\
6 7 8\\
0\\
X target, 0 origin. range 6 meters. 1d8 per direction, 2d6 per yards.

\linex

\textbf{Sprint Action}\\
x2 Movement. -1d6 to attack, -4 Defense, Distracted

\linex

\textbf{Disengage}\\
it costs 1 Action, you move 1 meter and you do not cause attacks of opportunity.

\end{textblock*}

~\newpage

\begin{textblock*}{19.5cm}(1cm,1cm) % box width, coord X, coord Y

\begin{tabularx}{0.95\textwidth}{llll}
\textbf{Weapon}&\textbf{Cost}&\textbf{Size/Damage} & \textbf{Range, List, Special}\\

Axe Hammer& 16 & M/1d6 T/B& \textbf{Axes}\\
Bastard sword& 35 & M/1d8-1d10 S&\textbf{Swords}, 1d8 one-handed, 1d10 two-handed\\
Battle Axe& 10 & M/1d10 S&\textbf{Axes}\\
Brandistocco& 10 & M/2d4 P/S& \textbf{Spear}, Counter-Charge, Long Weapon\\
Broadsword& 12 & M/2d4 S&\textbf{Swords}\\
Composite Longbow& note*& G/Arrows& 36 meters, \textbf{Bows}\\
Composite Shortbow& note*& M/Arrows& 20 metres, \textbf{Bows}\\
Cudgel& 1& P/1d6 B& \textbf{Simple Weapons}, \textbf{Skull Breaker}\\
Dagger& 2& P/1d4 P& 6 meters, \textbf{Simple Weapons}, \textbf{Light Weapons}, \textbf{Thrown Weapons}\\
Double Flail& 90 & M/1d10 B& \textbf{Whirling Balls}, \textbf{Double Weapons}\\
Estoc& 25& G/1d8 P& \textbf{Spears}, Long Weapon\\
Falchion& 75 & M/2d4 S& \textbf{Graceful Weapons}, \textbf{Spears}, ED7\\
Flail& 8& M/1d8 B& \textbf{Whirling Balls}, \textbf{Skull Breaker}\\
Great Cudgel& 2& M/1d8 B&\textbf{Skull Breaker}\\
Great Double Axe& 25 & G/1d12 S& \textbf{Axes}, \textbf{Double Weapons}, Long Weapon\\
Halberd& 10 & G/1d10 P/S& \textbf{Lance}, \textbf{Spear}, Counter-Charge, Long Weapon, ED9 \\
Hand Axe& 6 & M/1d6 S& 6 m, \textbf{Axes}, \textbf{Thrown Weapons}, Versatile\\
Heavy crossbow& 50 & G/Bolts& 30 meters \textbf{Crossbows}\\
Heavy Flail& 15 & M/1d10 B& \textbf{Whirling Balls}\\
Heavy Mace& 5& M/1d8 B/S& \textbf{Skull Breaker}\\
Heavy Pike& 8& G/1d6 P&\textbf{Weapons of Death}, Long Weapon\\
Infantry spear& 2& M/1d8 P&3 m, \textbf{Lance}, Long Weapon, Countercharge\\
Javelin& 1& P/1d6P& 12 meters, \textbf{Spears}, \textbf{Thrown Weapons} \textbf{Simple Weapons}\\
Katana& 300& M/1d10 S& \textbf{Swords}, \textbf{Lethal Weapons}, ED9\\
Light crossbow& 35 & P/Bolts& 15 meters, \textbf{Simple Weapons}, \textbf{Crossbows}\\
Light Mace& 3& P/1d6 B/S& \textbf{Simple Weapons}, \textbf{Light Weapons}, \textbf{Skull Breaker}\\
Light Pike& 4& M/1d4 HP&\textbf{Weapons of Death}\\
Longbow& 75 & G/Arrows& 20 meters, \textbf{Bows}\\
Longsword& 15 & M/1d8 S&\textbf{Swords}\\
Machete& 10 & M/1d6 S&\textbf{Lethal Weapons}\\
Naginata& 8& G/1d12 S&\textbf{Lance}, Long Weapon, ED9\\
One-Handed Crossbow& 100& M/Bolts& 6m, \textbf{Crossbows}\\
Pole Glaive& 12 & G/1d10 P/S& \textbf{Lance}, Countercharge, Long Weapon, ED9\\
Punch/Barefoot& note*& P/1d4 B&Versatile\\
Quaterstaff& 3& M/1d6 B& \textbf{Simple Weapons}, Long Weapon, Versatile\\
Rapier& 20 & P/1d6 P& \textbf{Simple Weapons}, \textbf{Graceful Weapons}, Versatile\\
Scimitar& 15 & M/1d6 S&\textbf{Simple Weapons}, \textbf{Graceful Weapons}, Versatile\\
Scythe& 18 & G/2d4 P/S& \textbf{Weapons of Death}, Long Weapon\\
Shortbow& 30 & M/1d6 P& 15 m, \textbf{Bows}\\
Shortsword& 10 & P/1d6 P&\textbf{Simple Weapons}, \textbf{Swords}, Versatile\\
Sickle& 6& P/1d6 S& \textbf{Weapons of Death}\\
Sling& -& P/1d4 B& 10 m, \textbf{Thrown Weapons}\\
Spear& 10 & G/1d8 P&\textbf{Spear}, Long Weapon, Countercharge\\
Spiked Chain& 25 & G/2d4 P& 3 meters, \textbf{Whirling Balls}, Long Weapon\\
Spiked gauntlet& 5& P/1d4 P&\textbf{Stun Weapons}\\
Spiked Mace& 6& M 1d8 B/P& \textbf{Simple Weapons}, \textbf{Skull Breaker}\\
Trident& 15 & M/1d6 P/S& 3 meters, \textbf{Spears}, \textbf{Thrown Weapons}, Long Weapon, Countercharge\\
Truncheon& 1& P/1d6 B& \textbf{Stun Weapons}, non-lethal\\
Two-bladed sword& 100& G/1d8 S& \textbf{Dual weapons}, \textbf{Swords}\\
Two-handed sword& 50 & G/2d6 S&\textbf{Swords}\\
Urgrosh& 18 & M/1d6 T/P& \textbf{Lance}, \textbf{Dual Weapons}\\
Warhammer& 5& M/1d8 W/P& 6 m, \textbf{Skull Breaker}\\
Warmaul& 7& G/1d10 B& \textbf{Skull Breaker}\\
Whip& 1& M/1d3 S& \textbf{Whirling Balls}, Long Weapon\\
\end{tabularx}

\end{textblock*}

\begin{textblock*}{11.5cm}(1cm,24.5cm) % box width, coord X, coord Y

\begin{tabular}{llll}
\textbf{Project Name} & \textbf{Number/MO} & \textbf{Damage/Type} & Weight(kg) \\
Marble Marbles (slingshots) & 15/1 gp & 1d4 W & 0.2 \\
Crossbow bolts, light & 10/1 gp & 1d6 P & 0.1 \\
Heavy crossbow bolts & 3/1 gp & 1d10 P & 0.3 \\
Hunting Arrows & 20/1 gp & 1d6 P & 0.1 \\
War Arrows & 10/1 gp & 1d8 P & 0.2 \\
Rock (slingshot) & - & 1d2 W & 0.2 \\
\end{tabular}

\end{textblock*}

\begin{textblock*}{8cm}(12.7cm,24.5cm) % box width, coord X, coord Y
\textbf{Carrying Capacity and Armor}\\
The CoC is equal to 9 (P), 16 (M), 25 (G) + Strength + Constitution.\\
A Light Weapon has Encumbrance 1, Medium has 2, Large has 4.
\end{textblock*}

~\newpage

\begin{textblock*}{15cm}(1cm,1cm) % box width, coord X, coord Y

\begin{tabular}{llllllll}
\textbf{Armour} & \textbf{Cost (gp)} & \textbf{Defence} & \textbf{Penalty Skill} & \textbf{Type} & \textbf{Move} & \textbf{Magic Test}&\textbf{Encumbrance}\\
\hline
Padded & 5 & 1 & 0 & L & 0 			& NO&2\\
Leather & 10 & 2 & 0 & L & 0		& YES&2\\
Studded Leather & 25 &3 & 0 & L & 0 & YES&2\\
Chain shirt & 15 & 4 & -1 & M & 0 	&+2&4\\
Scales & 50 & 5 & -1 & M & 0 		&+2&4\\
Chain Rings & 150 & 6 & -1 & M & 0 	&+2&4\\
Breastplate & 200 & 6 & -2 & M & 0 	&+2&4\\
Bands & 250 & 7 & -2 & P & 0 		&+1&8\\
Half Armour & 1200 & 8 & -2 & P & 1 &+1,2&8\\
from Field& 1400 & 9 & -3 & P & 2 	&+1,2&8\\
Complete & 1500 & 10 & -4 & P & 3 	&+1,1&8\\
\end{tabular}

\linex

\begin{tabular}{lccccc}
\textbf{Shields} & \textbf{Cost} & \textbf{Defense} & \textbf{TC Penalty} & \textbf{Try Magic} & \textbf{Type}\\
\hline
Light wooden shield 	 & 	3 mo  	&  1	& 0& YES	& L\\
Light Metal Shieldo 	& 	9 mo  	&  1	& 0& YES  	& L\\
Medium wood shield		 &	5 mo 	&  2	& 0& +2		& M\\
Medium metal shield	 	 &	12 mo  	&  2  	& 0& +2  	& M\\
Medium metal shield 	 & 	9  mo  	&  3 	& 1& +1,2  	& P\\
Heavy metal shiel		 & 	20 mo  	&  3	& 1& +1,2  	& P\\
\end{tabular}

\linex

\textbf{Armor and Shield Encumbrances}\\
Light armor has encumbrance 2, medium 4, heavy 8.\\
A light shield has encumbrance 1, medium 2, heavy 4.

\linex

\textbf{Times to put on and take off the armor}\index{Table of times to put on and take off the armor}\\

\begin{tabular}{llll}
\textbf{Type of Armor}& \textbf{Put On} & \textbf{quickly} & \textbf{Remove}\\
Shield & 1 action & - & 1 action\\
Padded, Leather, Reinforced Leather & 1 minute & 3 rounds & - \\
Giaco di Maglia & 1 minute & 5 rounds & 5 rounds\\
Scales, Rings, Breastplate, Bands & 4 minutes & 1 minute{*} & 1 minute\\
Half Armor, Field, Complete & 4 minutes{*}{*}& 4 minutes{*}& 1d4+1 minutes\\
\end{tabular}

\end{textblock*}

\begin{textblock*}{12cm}(1cm,14.7cm) % box width, coord X, coord Y

\begin{tabular}{lllll}
\hline
\textbf{Mount}&\textbf{Cost}&\textbf{Move}&\textbf{Load}&Km/h\\
&(\textbf{mo})&&&\\
Donkey or Mule&8&12m&210kg&6km\\
Camel&50&15m&240kg&8km\\
Galloping Horse&75&18m&240kg&12km\\
Warhorse&400&18m&270kg&9km\\
Draft Horse&50&12m&270kg&6km\\
Elephant&200&12m&660kg&6km\\
Mastiff&25&12m&97,5kg&6km\\
Pony&30&12m&112.5kg&6km\\
Cart/Wagon & 15/30 gp & 9/12 m &150/600kg & 3/6km \\
\end{tabular}

\linex

\begin{tabular}{ll}

\textbf{Container}&\textbf{Capacity}\\
Ampoule or Mug&0.5 liters of liquid\\
Barrel& 160 liquid liters, 4 cubes of 30 cm\\
Bag& 1 cube of 10cm/3kg of items\\
Bottle& 1 liter of liquid\\
Jug or Carafe&4 liters of liquid\\
Basket& 2 cubes of 30 cm/20 kg of objects\\
Vial & 120ml liquid\\
Chest& 12 cubes of 30cm/150kg of items\\
Wineskin & 2 liters of liquid\\
Bag& 1 cube of 30 cm/15 kg of objects\\
Bucket & 12 liters of liquid, 1 cube of 25 cm\\
Iron Vase & 4 liters of liquid\\
Backpack*& 1 cube of 30 cm/15 kg of items\\
\end{tabular}

\linex


\begin{tabular}{l|cc|c}
	\textbf{Source of} &\multicolumn{2}{c}{\textbf{Radius in meters}}& \textbf{Duration} \\
	\textbf{Light}& \textbf{Light} & \textbf{Dim Light} &\\
	Candela & 1 meter & - & 1 hour\\
	Torch & 3 meters & 6 meters & 1 hour\\
	Lantern & 3 meters & 6 meters & 3 hours \\
	\multicolumn{4}{c}{\textbf{spells}}\\
	Light & 3 meters & 6 meters &3T \\
	Daylight & 6 meters & 12 meters & 1 hour \\
\end{tabular}

\end{textblock*}

\begin{textblock*}{6cm}(13.4cm,14.7cm) % box width, coord X, coord Y

\begin{tabular}{ll}
\textbf{Item}&\textbf{Cost}\\
\textbf{Beer}&\\
Mug&4 mr\\
Carafe (4 litres)&2 but\\
\textbf{Dishes} &\\
Banquet (per person)&10 mo\\
Meat, 1 piece&3 sp\\
Cheese, 1 piece&1 but\\
Bread (per loaf)&2 mr\\
\textbf{Inn (per day})&\\
Sleazy&7 mr\\
Poor&1 but\\
Modest&5 sp\\
Wealthy&8 ma\\
rich&2 mo\\
Aristocratic&4 mo\\
\textbf{Meal (per day)}&\\
Shabby&3 mr\\
Poor&6 mr\\
Modest&3 but\\
Wealthy&5 but\\
Rich&8 but\\
Aristocrat&2 mo\\
\textbf{Wine}&\\
Voucher (bottle)&10 gp\\
Common (jug)&2 but\\
\end{tabular}

\end{textblock*}

~\newpage

\begin{textblock*}{4cm}(1cm,1cm) % box width, coord X, coord Y
{\textbf{Skills}\\
	
\textbf{Strenght}	\\
Climbing\\
Intimidate\\
Swimming\\
Jumping\\
\textbf{Dexsterity}\\
Acrobatics\\
Escape Artist\\
Fairy Hands\\
Move Silently\\
Hide in Shadow\\
Use Rope\\
\textbf{Intelligence}\\
Arcana\\
Craft*\\
Knowledge*\\
Disable Device\\
Herbalism\\
Falsify\\
Appraise\\
\textbf{Wisdom}\\
Riding\\
\textit{Awareness}\\
Animal Handling\\
Nature\\
Orientation\\
Sense Emotions\\
First Aid\\
Track\\
Survival\\
\textbf{Charisma}\\
Diplomacy\\
Entertain\\
Deceive\\
Local lore\\
}

\linex

\textbf{Recognize a spell}\\ Arcana DC 11 + spell level. 1 reaction

\linex

\textbf{Evaluate} 3 Actions : DC 12 + item rarity, + 2 common, 4 uncommon, 6 rare, 12 very rare, 16 legendary. \\
With a score of 6 it costs 2 Actions, with a 12 it costs 1 Action.

\end{textblock*}


\begin{textblock*}{14.5cm}(5.5cm,1cm) % box width, coord X, coord Y
\textbf{Golden Rules}\\

{\textbf{The 6s explode}} - if you roll 6, you add and fold\\
\textbf{1's are bad luck}, if you roll 1 it's zero\\
\textbf{Trust your luck}. -4 proficiency/characteristic points = +1d6\\
\end{textblock*}


\begin{textblock*}{7.4cm}(5.3cm,3.2cm) % box width, coord X, coord Y
\textbf{First Aid}\\
DC 12 + INT(-HP) stabilize at 0 HP\\
2 minutes/1 p6: DC 15 recover 1d4 HP\\
+2 ST Fortitude Poison\\
DC 12+2xBleed -1 Bleed

\linex

\textbf{Intimidate}\\
2 Actions. p12 1 Action. Intimidate is opposed to the Will save (CHA). If the saving throw fails, the opponent until the end of the next round has -1 to attack rolls and -1 to defense against that opponent only.\\
If the user attempting the Intimidate check fails with a successful critical failure then he must make a Will save with a Charisma modifier at DC 10 + the opponent's Challenge Rating (or level) or suffer the same penalties as if he had been intimidated.
If the opposed roll succeeds with a critical success and the opponent fails the saving throw, the duration of the effect lasts until the end of the fight.

\linex

\textbf{Climbing - Climbing}\\
\textit{You have Armor penalties}

\begin{tabular}{ll}
\textbf{Example of Surface} & \textbf{DC}\\
Movement only halved & -2d6\\
Slippery surface&+5\\
Rough with handholds, protruding bricks&10\\
Tree, a rope without knots&15\\
Smooth wall with grips &20\\
Perimeter wall very few holds&25\\
Natural wall without holds&30\\
Lean against 2 opposite walls&-10\\
Lean on 2 corner walls&-5\\
You can use a string&-8\\
\end{tabular}

\textbf{Double difficult terrain}. If you fail 10+ you fall, DC itself Reflex save to grab yourself.

\linex

\textbf{Recognize a monster} 1 Action\\
Arcana: Giants, Constructs, Spirits, Monstrosities\\
Aberrations, Dragons\\
Planes: Elementals\\
Occult: Fiends, Spirits, Undead\\
Religion: Spirits, Undead, Celestials\\
Dungeons: Aberrations, Monstrosities, Oozes, underground creatures\\
Nature: Beasts, Plants, Fairies\\
\textbf{DC} = Challenge Rating + 10

- \textit{within \textbf{2}}: name, type, main feature|
- \textit{over \textbf{7}}: best saving throw, a resistance/immunity to Conditions, a vulnerability to Conditions, typical attack|
- \textit{over \textbf{12}}: worst Saving Throw, 1 resistance/immunity to Conditions, 1 immunity to Damage, a vulnerability to Conditions, 1 vulnerability to a type of Damage|
- \textit{over \textbf{15}}: 2 immunities to Conditions, 1 immunity to Damage, one vulnerability to Conditions, 1 vulnerability to Damage type|
- \textit{over \textbf{17}}: relative degree of challenge|
- \textit{over \textbf{20}}: attack and special defenses|

\end{textblock*}



\begin{textblock*}{7cm}(13cm,3.2cm) % box width, coord X, coord Y
	
\textbf{Opposed Check}\\
Whoever takes the Test must roll at least 10 + Proficiency/Saving Throw + Statistics + Skill

\linex	
	
\textbf{Identify Potions}\\
Herbalism at DC 12 + plant rarity factor. 1 Action every 10 DC, 6p every 15 DC, 12p every 20 DC

\linex

\textbf{Recognize magic item}\\
1 minute DC 30. Arcana 6p costs 5 min., 12p costs 1 min., 18p costs 1 Round.
\linex

\textbf{Jump} 1 Action\\
\textit{You have Armor penalties}

\textbf{Long Jump Distance}: 30cm per result\\

\textbf{Distance jumped up}: 10cm per result\\

Run up 3 meters otherwise half.

\linex

\textbf{Fall Damage}: H(m)/3xD6. For every 3 dice over 20, add 6 damage (X/3)d6+(X/3-20)*6. Prone. Acrobatic Check DC 15 1/2 damage within 9m. Falls onto soft surfaces (soft ground, mud, etc.) -1d6 damage.

\linex

\textbf{Swimming}\\
\textit{Penalty due to Armor on Strength}\\
Calm water DC 10.\\
White water has DC 15\\
Stormy Waters DC 20

\linex

\textbf{Survival}
\begin{tabular}{ll}
Basic Difficulty & DC 10\\
If the ground is very soft& DC +5\\
If the ground is soft& DC +10\\
If the ground is stable& DC +15\\
If the ground is hard& DC +20\\
Every 3 creatures chased& DC -1\\
Depending on size & DC +-8\\
Every past 24 hours&DC +2\\
Every hour of rain&DC +4\\
Poor visibility&DC +2\\
Try to hide the traces&DC +5\\
\end{tabular}\\

\linex

\textbf{Escape Artist}\\
1 Action every 10 of DC. 6p 1 Action 15 of DC, 12p 1 Action 20 DC.

\end{textblock*}

~\newpage

\begin{textblock*}{5cm}(1cm,1cm) % box width, coord X, coord Y
\textbf{Magic test}\\
3d6 + 1d6 every 2 Magic List know,  and ignore 1 for each Adept of Magic in the magic list of spell\\
Critical Failure: two 1s, one 1 and two 2s\\


\linex

\textbf{Distracted}\\
You are Distracted if you: Conceal spell casting, Impeded, Disturbed, Threatened, Bleeding, Under Attack.\\

\linex

\textbf{Magic Points}\\
mod. Feature + \\

\begin{tabular}{ll|ll}
\textbf{CM} & \textbf{P.M}& \textbf{CM} & \textbf{P.M}\\
	1&	2 	&11&43\\
2&	4	&12&47\\
3&	8	&13&50\\
4&	10	&14&54\\
5&	16	&15&58\\
6&	19	&16&62\\
7&	23	&17&71\\
8&	27	&18&76\\
9&	36	&19&82\\
10&	41	&20&89\\
20+&prev.+ 4&&\\
\end{tabular}

\linex

\textbf{Saving Throw Spell}\\
DC = 10 + Magic Competence + ability modifier per spell + 1 x Adept of Magic feat taken in that Magic List +1 x Critical in Magic Test

\linex

\textbf{Item Magic Saving Throw}\\
DC = 10 + 2 x manifested spell level

\linex

\textbf{Saving Throw Monster Spell}\\
DC is 10 + 2 x spell level + Intelligence

\linex

\textbf{When you have < 50\% Magic Points} each spell must be done with a Magic Test.

\linex

\textbf{Automatic Critical Success}: x2 cumulative Magic Point cost. Ex. 4,8,16,32..

\linex

\end{textblock*}


\begin{textblock*}{13.5cm}(6.5cm,1cm) % box width, coord X, coord Y
\textbf{Follower}\\
2 Common traits with Patron. If you are a follower, you gain +1d6 on Magic Checks in the Patron's favored school. You can use the Patron's favored energy in your spells.\\

\linex

\textbf{Devoted}\\
3 Traits in common with Patron. A Devotee adds +1d6 to the Magic Test in the Patron's favored schools and ignores one die rolled in the Magic Test. You must use the Patron's favored energy in your spells.

\linex

\textbf{Magic Test Critical Failure - 3d6 -1d6 x Crit. mins 1d6}
\begin{tabularx}{0.95\textwidth}{lX}
1 & For 1 day you are no longer able to channel magical energies. You cannot cast spells unless you make a critical magical success on the Magic Test\\
2 & Increase your Fatigued status by 2 ranks\\
3 & You exhibit minor body modification\\
4 & You are hit by a thundering column of Light and Void. In a 10-foot radius centered on you, anyone must make a DC 15 Reflex saving throw to halve or take 1d6 points of damage per spell level\\
5 & For 3 rounds you are under the influence of the Confusion spell\\
6 & You are paralyzed for 3 rounds\\
7 & You are teleported 3d10 meters in a random direction\\
8 & Only you are shrouded in impenetrable magical darkness for 6 rounds\\
9 & You become invisible and unable to speak for 6 rounds\\
10 & You can't speak well, you stutter. Each spellcasting forces you to pass a Magic Test. Duration 3 rounds\\
11 & The next spell you cast has effects that are minimized if possible\\
12 & All creatures within 60 feet know exactly where you are and what you were trying to do.\\
13 & Your heartbeat is like the beating of a drum, it can be heard within 36 meters\\
14 & All your body hair falls out, luckily it can grow back\\
15 & Every object you hold in your hand falls to the ground\\
16 & Gain 2d6 Magic Points\\
17 & An anvil falls, 3d6 damage Reflex save DC 15 to halve, on one random creature, excluding you, within twenty feet\\
18 & Creatures, excluding you, within 20 feet of you take 3d10 unresistible damage
\end{tabularx}

\linex

\textbf{Maximum Spell Level that can be cast}

Add to CM the times you took Adept of Magic and divide the result by 2. E.g. CM=8, Adept of Magic taken 4 times, (8+4)/2=6, or CM=13, Adept of Magic 1 time, (13+1)/2=7 spell level.


\linex

\textbf{Alter Magic}

- \textbf{Punishing Spells}: 2 times spell cost, +1 die in the Magic Test. Reaction

- \textbf{Effective spells}: 3 times spell cost, -1 die in the Magic Test. Reaction

- \textbf{Ethereal Magic}\index{Ethereal Magic}: +3 Magic Points, hit ethereal or incorporeal creatures. Immediate Action.

- \textbf{Magic Sacrifice}\index{Magic Sacrifice}: -4 HP +1 Magic Point. You can't sacrifice more than half your current Hit Points at a time. Immediate Action.

- \textbf{Pitiful Magic}\index{Pitiful Magic}: +3 Magic Points and temporary damage. 1 Action.

- \textbf{Targeted Magic}\index{Targeted Magic}: every two times Adept of Magic exclude 1 target from spell. Cost 2 Magic Points per excluded creature. 1 Action.

- \textbf{Far Magic}\index{Far Magic}: +1 Magic Points increase the casting distance up to 9 meters. 1 Action.

- \textbf{Increase time}\index{Increase time} +1 Action, -1 Magic Point

- \textbf{Circle of Power}\index{Circle of Power}: see description

\end{textblock*}

~\newpage

\end{document}
