\documentclass[landscape,10pt,a4paper]{article}
\usepackage[margin=0.5cm,landscape]{geometry}
\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{multicol, tabularx,multirow}
\usepackage{multirow}
\usepackage{tabularray}
\usepackage{tabulary}
\usepackage{xcolor}
\usepackage{xltabular}
\usepackage{xr}
\newcolumntype{T}{>{\scriptsize}l} % define a new column type for \tiny
\usepackage[many]{tcolorbox}
\usepackage[absolute,overlay]{textpos} % Load textpos package BEFORE geometry
\geometry{verbose,tmargin=1.5cm,bmargin=1.5cm,lmargin=1.5cm,rmargin=1.5cm}

% Define colours
\definecolor{headercolor}{RGB}{70,130,180} % SteelBlue
\definecolor{boxcolor}{RGB}{220,220,220} % Light gray

\definecolor{myblue}{RGB}{70,130,180}

\newtcolorbox{mybluebox}[1][]{
colback=myblue,
colframe=myblue,
boxrule=0.4pt,
arc=3mm,
auto outer arc,
enhanced jigsaw,
width=\linewidth, % column width
coltitle=black,
toptitle=1mm, % top margin
bottomtitle=1mm % bottom margin
}
\newcommand{\header}[1]{\textbf{\color{headercolor}\large #1}}
\newcommand{\subheader}[1]{\textbf{\small #1}}
\newcommand{\checkthing}[1]{$\square$ #1}
\setlength{\columnsep}{10pt}
\setlength{\columnseprule}{0.4pt}

\newtcolorbox{dmbox}[1][]{
colback=boxcolor!30,
colframe=headercolor,
fonttitle=\bfseries,
#1
}

\externaldocument{OBSSv2-eng}

\begin{document}
\pagestyle{empty}



\begin{multicols}{3}

\footnotesize

\begin{dmbox}[title=Conditions - page \pageref{conditions}]

\begin{itemize}[leftmargin=0.5cm,itemsep=-1pt,parsep=0pt]
\item \textbf{Damage category increase}: 1d4 > 1d6 > 1d8 > 1d10/d12 > 2d6 - 2d8 > 2d10 > 3d6 > 3d8 > 3d10
\item \textbf{Blinded}:\index{Blinded}. You cannot see. -2 Strength and Dexterity-based skills. Everyone is invisible. Terrain is always difficult (Acrobatics DC 12 to move normally). -1d6 to hit, +1d6 to be hit.
\item \textbf{Exhausted}: No running, no charging. Penalty to TC, Defence, TS and Checks.
\item
\begin{tabular}{lcl}
\textbf{Conditions}& \textbf{Penalty/Mov/Comp.}&\textbf{Rec.}\\
\hline
Exhausted &1/-/-&1h\\
Fatigued 2&2/2m/-4&1h\\
Fatigued 3&4/3m/-6&8h\\
Fatigued 4&6/6m/-8&12h\\
Fatigued 5&Unconscious&6h\\
Fatigued 6&Death&--
\end{tabular}
\item \textbf{Grabbed}\index{Grabbed}: No movement. Can push. 2 actions to break free (TS Tempra + Strength against Athletics check, +1d6 for size difference). -2 Defence, Distracted. Only small or natural weapons.
\item \textbf{Drowning/Holding breath}: Round 10+10 x Cos. 1 Action = -1 Round. After TS Fortitude DC 12 each round to continue holding breath. Each round, the DC increases by 2. See page 243
\item \textbf{Deafened}: Distracted when casting spells with at least verbal components.
\item \textbf{Blocked}: see Grapple. -4 to Defence and Reflex saves. Check Magic with critical success for spells. -1d6 TC
\item \textbf{Coup de Grâce}:: 3 actions, 3 critical hits. Defenseless target.
\item \textbf{Confused}: when attacked, attacks last creature. Each round rolls

\noindent\begin{tabularx}{0.99\textwidth}{lX}
\hline
\textbf{d10} & Behaviour\\
\textbf{1} & The creature uses all its Actions to move in a random direction. To determine the direction, roll a d8\\
\textbf{2-5} & The creature does nothing for the entire round\\
\textbf{6} & The creature attacks itself and ends the round.\\
\textbf{7-8} & The creature attacks a randomly determined creature within 1 Movement Action. If it was hit in the previous round, it attacks the creature that hit it. Once the attack is made, the round ends.\\
\textbf{9-10} & The creature can act and move normally.\\
\end{tabularx}

\item \textbf{Distracted}: distracted, hindered, disturbed, bleeding, under attack, you must make a Magic Check
\item \textbf{Running}: -4 Defence, -1d6 TC until the start of the next round
\item \textbf{Flanking}: +2 to Hit or Defence.
\item \textbf{Unprepared / Surprised} -2 to Defence and Reflex Saves. No Actions, Reactions
\end{itemize}

\end{dmbox}



\begin{dmbox}[title=Conditions]
\begin{itemize}[leftmargin=0.5cm,itemsep=-1pt,parsep=0pt]

\item \textbf{Disabled}: No actions or reactions. You are unprepared
\item \textbf{Struggling}: see Grappled
\item \textbf{Defenseless} asleep, unconscious, dying, at the mercy of opponents. No Actions or Reactions, +1d6 if attacked. Not aware, drops items and falls prone. Reflex and Fortitude saves fail. No Dexterity to Defence.
\item \textbf{Hindered}: difficult terrain, no running, no charging, -2 TC, -2 Defence, Distracted.
\item \textbf{Invisible}: -1d6 to TC, +1d6 to opponent's TC.
\item \textbf{Dying}: -1 hp per round
\item \textbf{Nauseated}: -1d6 TS, TC, Checks
\item \textbf{Paralysed}: No Actions or Reactions. +1d6 to opponents' TC. Reflex TS failure. NO Dexterity to Defence. It is difficult terrain.
\item \textbf{Fear, Frightened}: -1d6 to TC and TS against those who frighten them.
\item \textbf{Unconscious}: see Defenceless
\item \textbf{Prone}\index{Prone}: -4 TC, -4 Defence. 1 Action
\item \textbf{Stunned/Unconscious}: see Defenceless
\item \textbf{Holding breath}: see \textbf{Drowning/Holding breath}
\item \textbf{Restricted} : -1d6 TC, -4 Defence.
\item \textbf{Bleeding}: at the start of the round. First Aid with DC 12, 2 Actions, +2 for +1 Bleeding.

\end{itemize}

\end{dmbox}

\begin{mybluebox}\textbf{Fate Points}: (20-Level)/5 - page \pageref{fatepoints}\end{mybluebox}

\begin{mybluebox}\textbf{Death}: -10-(COS*2) - page \pageref{dying}\end{mybluebox}

\begin{dmbox}[title=Multiple Attacks - page \pageref{multiple attacks melee}]
The first attack action has no penalty, while the second attack action has a cumulative -5 to hit per attack. This also applies to spell attacks.
\end{dmbox}

\begin{dmbox}[title=Prepare Defence - page \pageref{prepareladifesa}]

Using \textbf{1 Action} increases your \textbf{Defence} by 1.

If the weapon has the \textbf{Parry} trait, the Prepare Defence bonus increases by 1.
\end{dmbox}

\begin{dmbox}[title=Cover - page \pageref{copertura}]
\noindent\begin{tabular}{l|c}
\textbf{Coverage} & \textbf{Defence Bonus}\\
\hline
Light (at least 50\% visible) & +2\\
Medium (visibility between 50\% and >30\%) & +4 \\
Complete (between 30 and 10\%) & +8 \\
\end{tabular}\\

Half of the bonus applies to Reflex Saves.

Each creature of the same size as the opponent in line that \emph{covers} the target increases the coverage provided by one degree.

\end{dmbox}

\begin{mybluebox}\textbf{Powerful Strikes}: +1 damage - 2 TC. MAX AC/4 - page \pageref{powerfulstrikes}\end{mybluebox}


\begin{dmbox}[title=Combat Mastery - page \pageref{combatmastery}]
\noindent\begin{tabular}{l|c}
\textbf{Bonus} & \textbf{Penalty}\\
\hline
+1 Defence & every -2 Hit Roll\\
+1 Hit Roll & every -2 to Defence
\end{tabular}\\

The bonus cannot exceed Weapon Proficiency/4
\end{dmbox}

\begin{dmbox}[title=Charge - page \pageref{charge}]

The opponent must be within 2 Movement Actions and no less than 3 metres away. 

You gain +1d6 to Hit, -4 to Defence until the start of your next round, the attack following the first takes a -10 to hit and any subsequent attacks take -15, 20...

Movement and attack cost 2 Actions. No other penalties are considered for running beyond those indicated.

The Charge Action brings you into melee with your opponent. If made with a long weapon, the attack is made at a distance of 2 metres and then ends in contact with the opponent.
\end{dmbox}

\begin{dmbox}[title=Opportunity Attack - page \pageref{attaccoopportunita}]
You must have the \textbf{Opportunistic} Feat.

The creature leaves or crosses the melee zone or casts a spell. This attack is a Reaction.
\end{dmbox}

\begin{dmbox}[title=Actions per Round - page \pageref{actionsintheround}]

\noindent\begin{tabular}{ll}
\textbf{What you do} & \textbf{Actions}\\
\hline
Make an attack& 1\\
Make two attacks& 2\\
Make more than two attacks& 3\\
Draw or sheathe a weapon or shield& 1\\
\hline
Take a Movement Action &1*\\
Dash & 1\\
Stand up from prone& 1\\
\hline
Help someone& R\\
Perform a skill check& 1*\\
Recognise a creature& 1\\
Hide& 1\\
\hline
Mount or dismount a mount& 2\\
Break down a door by ramming/kicking it& 1\\
Force a door open with a crowbar& 2\\
\hline
Search your backpack& 2\\
Take something from your belt or from a nearby location & 1\\
Use an item held in your hand& 1\\
\hline
Drink a potion held in your hand& I\\
Make someone else drink a potion & 2\\
\hline
Throw an item held in your hand& R\\
Throw yourself prone on the ground& R\\
\hline
Cast a spell*& 2\\
Concentrate on a spell& 1\\
Interrupt your own spell & I\\
Recognise a spell& R\\
Use a magic item& 2\\
\hline
Exchange dialogue with someone& 3*\\
Exchange a few words with someone& 0*\\
\hline
Prepare Defence & 1\\
Total Defence & 2\\
Disengage & 1\\
Precise Strike & 2\\
\hline
Disarm & 2\\
Feint & 1\\
Push & 2\\
Grab opponent & 2\\
Knock down opponent & 2
\end{tabular}
\end{dmbox}

\begin{dmbox}[title=Damage Explosion - page \pageref{damageexplosion}]
If the weapon's damage roll is the maximum value (min 8), roll the die again and add the value (of the die only).
\end{dmbox}

\begin{dmbox}[title=Standing Up From Prone - page \pageref{alzarsidaprono}]
\textbf{}\\
1 Action. -4 Defence/To Hit.

Acrobatics DC 13 1 Immediate Action. If you roll three 1s, you lose the round. 
\end{dmbox}



\begin{dmbox}[title=Dash Action - page \pageref{azionediscatto}]
Costs 1 Action. You make a double movement, until the start of the next round you have -1d6 on your Hit Roll, -4 Defence and you are Distracted.
\end{dmbox}

\begin{dmbox}[title=Defence Against Surprise - page \pageref{defenceandattack}]
You have -4 to Defence and -4 to Reflex Saves.
\end{dmbox}

\begin{dmbox}[title=Touch Attack - page \pageref{difesaatocco}]
You have +1d6 to your Attack Roll
\end{dmbox}

\begin{dmbox}[title=Critical Hit - page \pageref{criticalhit}]
Whenever you hit, roll an additional weapon die and do not add anything else for every two times you rolled a 6 on your Attack Roll. Or every 8 margin (Critical Hit Variant)
\end{dmbox}

\begin{dmbox}[title=Total Defence - page \pageref{totaldifence}]
2 Actions, NO Attack, NO Spells. Difficult Terrain. No opportunity attacks. +4 to Defence.
\end{dmbox}

\begin{dmbox}[title=Disengage - page \pageref{disingaggiare}]
Costs 1 Action, you move 1 metre and do not cause attacks of opportunity
\end{dmbox}

\begin{dmbox}[title=Scatter Ranged Weapons - page \pageref{attackswithscatterweapons}]
In this diagram, \textbf{0} is the thrower and \textbf{X} is the target.\\

\noindent\begin{tabular}{c|c|c}
8 &1 &2\\
\hline
7 &\textbf{X}& 3\\
\hline
6 &5& 4\\
\hline
&0&\\
\end{tabular}\\

If the Hit Roll misses by at least 5, roll 1d8 to determine the direction and roll 2d6 to determine the distance from the target.
\end{dmbox}

\begin{dmbox}[title=Vision - page \pageref{visionandlight}]

A Blinded creature suffers a -1d6 penalty on Awareness checks and a -2 penalty on Strength and Dexterivity checks, and automatically fails any Awareness check that depends on sight.

\begin{itemize}[leftmargin=0.5cm,itemsep=-1pt,parsep=0pt]
\item Using Darkvision / Twilight Vision: \textbf{Survival} checks to search for traps or \textbf{Perception} checks that rely solely on sight take a -2 penalty.
\item Fighting in \textbf{Low Light}': -1 to hit
\end{itemize}
\end{dmbox}

\begin{dmbox}[title=Light Sources - page \pageref{light sources}]

\noindent\begin{tabular}{l|cc|c}
\textbf{Source of} &\multicolumn{2}{c}{\textbf{Range in metres}}& \textbf{Duration} \\
\textbf{Light}& \textbf{Light} & \textbf{Dim Light} &\\
Candle & - & 1 metre & 1 hour\\
Torch & 3 metres & 6 metres & 1 hour\\
Lantern & 6 metres & 12 metres & 3 hours \\
\multicolumn{4}{c}{\textbf{Spells}}\\
Ljust's Tear & 1 & - & 10 rounds\\
Light & 3 metres & 6 metres &30 min. \\
Daylight & 6 metres & 12 metres & 1 hour 
\end{tabular}
\end{dmbox}

\begin{dmbox}[title=Rest 8 hours - page \pageref{recuperarepf}]
Each night of rest (at least 8 hours) you recover Hit Points equal to your Constitution*Level, with a minimum HP equal to your Level.
\end{dmbox}


\begin{dmbox}[title=Non-lethal damage - page \pageref{nonlethalhitpointrecovery}]
Every hour, you recover your Constitution value in non-lethal HP (stun damage) lost, with a minimum of 1 HP.
\end{dmbox}



\begin{dmbox}[title=Carrying Capacity (CdC) - page \pageref{carryingcapacity}]
The Carrying Capacity is equal to 6 (P), 12 (M), 24 (G) + Strength + Constitution.
\end{dmbox}


\begin{dmbox}[title=Golden Rules - page \pageref{goldenrules}]
{\textbf{6 explodes}} - if you roll a 6, add it up and roll again\\
The \textbf{1 are bad luck}, if you roll a 1 with the dice, it counts as zero\\
\textbf{Rely on luck}. Every 4 points between Basic or Active Skill or Characteristic = +1d6
\end{dmbox}



\begin{dmbox}[title=Difficulty and Skill - page \pageref{basedifficolta}]
\begin{tabular}{lll}
\textbf{Difficulty} & \textbf{Description} & \textbf{Skill} \\
5 & Extremely easy & None\\
10 & Easy & Poor\\
15 & Normal & Normal\\
20 & Difficult & Good\\
25 & Very difficult & Excellent\\
30 & Heroic & Excellent\\
35 & Almost impossible & Amazing\\
40 & Impossible & Epic\\
\end{tabular}
\end{dmbox}


\begin{dmbox}[title=Recognising a spell - page \pageref{recognising spell}]
Arcana DC 10 + spell level. 1 Reaction
\end{dmbox}


\begin{dmbox}[title=Recognising a magical item - page \pageref{recognisingmagicalitem} - \pageref{identify}]
Arcana DC 20. DC 25 to identify. Critical for curses
\end{dmbox}

\begin{dmbox}[title=Mounts/Cost/Movement - page \pageref{mountcost} - \pageref{table-mounts-and-vehicles} - \pageref{tipodimovimento}]

\begin{tabularx}{1\textwidth}{lllXX}
\textbf{Mount} & \textbf{Cost} & \textbf{CdC} & \textbf{Hourly speed} & \textbf{Km per day}\\
\toprule
Galloping Dog &25&30&6km & 36km \\
Saurov. Galloping&75&60&8km & 48km \\
War Saurov. &400&80&7km & 42km \\
Dwarf Saurov.&30&50&5km & 30km \\
Tiro Saurov.&50&70&6km & 36km \\
Camel&50&60&8km & 48km \\
Elephant&160&320&6km & 36km \\
Cart/Chariot &15/30 & &&
\end{tabularx}

\bigskip

\begin{tabular}{lccc}
\multirow{2}*{\textbf{Type of movement}} &
\multicolumn{3}{c}{\textbf{Movement}}\\
\cmidrule(lr){2-4} & 6m& 9m & 12m\\
\hline
\multicolumn{4}{c}{\textbf{Movement (Tactical)}}\\
Walking& 6m & 9m & 12m\\
Running (x2) & 12m& 18m& 24m\\
\multicolumn{4}{c}{\textbf{One minute (Local)}} \\
Walking & 36m& 54m& 72m \\
Running (x3) & 108m & 162m & 216m \\
\multicolumn{4}{c}{\textbf{One hour (By land)}} \\
Walking & 3km & 4km & 6km\\
Running (x3) & 9km & 12km & 18km \\
\multicolumn{4}{c}{\textbf{One day (By land)}}\\
Walking & 24km & 32km & 54km
\end{tabular}

\end{dmbox}

\begin{dmbox}[title=Standard size and capacity - page \pageref{sizeandcarry}]
\begin{tabularx}{0.95\linewidth}{llll}
\toprule
\textbf{Size}& \textbf{Dimensions} &\textbf{Squares}&\textbf{Capacity}\\
Minuscule & 25 x 25 &cm 1/4&0m\\
Small & 0.5 x 0.5 m & 1/2&1m\\
Medium & 1 x 1 m & 1&1m\\
Large & 2 x 2 m& 2x2&1m\\
Huge & 3 x 3 m & 3x3&2m\\
Mammoth & 4 x 4 m&4x4&2m\\
Colossal & 12 x 12 m&6x6&6m
\end{tabularx}
\end{dmbox}






\begin{dmbox}[title=Evaluate - page \pageref{evaluate}]
DC 12 + item rarity factor. Common +0, Uncommon +2, Rare +6, Very Rare +10, Legendary +16. 3 Actions
\end{dmbox}

\begin{dmbox}[title=Identify a natural potion or poison - page \pageref{identificarepozioni}]
This is possible with a Herbalism check equal to the DC of the plant's rarity factor, or the TS granted by the plant in the case of Poisons.

It takes 1 Action per 10 DC. With 6 in Herbalism, the time is 1 Action per 15 DC, with 12 points it is 1 Action per 20 DC to perform the check. If you fail with a critical failure, you have come into contact with/ingested part of the potion and suffer its effects.
\end{dmbox}



\begin{dmbox}[title=Skills - page \pageref{skillslist}]
\begin{tabularx}{0.95\linewidth}{ll}
\multicolumn{2}{c}{\textbf{Strength}}\\
Climbing & Intimidate\\
Swimming & Jumping\\
\multicolumn{2}{c}{\textbf{Dexterity}}\\
Acrobatics & Escape Artist\\
Juggling & Sleight of Hand\\
Stealth & Rope Use\\
\multicolumn{2}{c}{\textbf{Intelligence}}\\
Arcane & Craft\\
Knowledge*&Disable Devices\\
Herbalism&Fake\\
Languages&Appraise\\
\multicolumn{2}{c}{\textbf{Wisdom}}\\
Riding & Awareness\\
Animal Handling & Nature\\
Emotion Perception & First Aid\\
Tracking & Survival\\
\multicolumn{2}{c}{\textbf{Charisma}}\\
Diplomacy & Entertainment\\
Deception & Local Lore
\end{tabularx}
\end{dmbox}


\begin{dmbox}[title=Acrobatics - page \pageref{acrobatics}]
A successful Acrobatics check with DC 15 allows the character to reduce damage by 3 when falling within 6 metres (\textbf{Reaction}).

\textbf{Climbing Down or Up} Within 50 cm is difficult terrain, between 50 and 150 cm is doubly difficult terrain, beyond that is falling or climbing. Fall damage is 1d6 damage per 3 metres fallen. \index{Climbing Down and Up}

\textbf{Fall Damage}: H(m)/3xD6. For every 3 dice over 20, add 6 damage (X/3)d6+(X/3-20)*6. Prone. Acrobatics Check DC 15 1/2 damage within 9m. Falls on soft surfaces (soft ground, mud, etc.) -1d6 damage.
\end{dmbox}

\begin{dmbox}[title=Climbing/Climbing - page \pageref{climbing}]

Using a rope to climb\index{Descending with a rope}\index{Climbing a rope}, scaling or climbing is equivalent to moving in \textbf{double difficult terrain}.

If the check fails, the Action is consumed without moving. If you get a critical failure, you lose your grip and can make a Reflex Saving Throw at the same difficulty to grab onto something. If you fail the ST, you fall to the bottom.

The difficulties indicated are added together.

\medskip

\noindent\begin{tabularx}{1\linewidth}{Xl}
\textbf{Example of Surface} & \textbf{DC}\\
\toprule
Movement halved & -2d6\\
Slippery surface&+4\\
Rough wall with handholds, protruding bricks&+12\\
A tree, a knotless rope&+15\\
A wall with a few protruding bricks &+20\\
A wall with very few handholds&+25\\
A smooth natural wall with no handholds&+30\\
You can lean against two opposite walls&-8\\
You can lean against two corner walls&-4\\
You can use a rope&-8\\
\midrule
Use a rope to lower yourself&12\\
Use a rope to climb&15\\
The rope has knots & -3\\
\end{tabularx}

\medskip

In case of Critical Success, you climb as if it were difficult terrain and not doubly difficult terrain.

\end{dmbox}

\begin{dmbox}[title=Athletics - page \pageref{athletics}]

The \textbf{long jump distance} is equal to 30cm for the result obtained in the check, rounded to the nearest whole number. E.g. if in the jump test I jump 11, the jump will be 30cm*11=330cm=3 metres long, with 16 in the test it is 30cm*16=480cm=5m.

The \textbf{distance jumped in height} is equal to 10cm for the result obtained in the test.

In a \textbf{long jump}, the highest point of the jump is equal to 1/3 of the length jumped. If you perform a long jump of 3 metres, halfway through the jump you are 1 metre high.

If you do not have at least 3 metres of run-up, you jump half the distance. In the long jump, you jump at most your own movement and half the height.

Performing a jump from a standing position costs 1 Action. A jump performed within half of your movement (i.e. within 4 metres for a human) does not cost any Action, otherwise you consume one Action for Movement and one Action for Jumping.
\end{dmbox}



\begin{dmbox}[title=Following Tracks - page \pageref{tracking}]
The modifiers indicated apply to the \textbf{base difficulty of 15}.\\

\noindent\begin{tabular}{ll}
If the terrain is very soft& DC -4\\
If the terrain is stable& DC +5\\
If the terrain is hard& DC +10\\
Depending on size& DC $\pm4$\\
Every 3 creatures being pursued& DC -2\\
Every 24 hours passed& DC +4\\
Every hour of rain& DC +4\\
Poor visibility& DC +2\\
Trying to hide tracks& DC +4\\
\end{tabular}
\end{dmbox}

\begin{dmbox}[title=Recognising monsters - page \pageref{recognisingmonsters}]

To recognise a monster, make a Knowledge check, which costs 1 action, on:

\medskip

\emph{Arcane}: Giants, Constructs, Spirits, Monstrosities, Aberrations, Dragons

\emph{Plane}: Elementals

\emph{Occult}: Foul (Devils and Demons), Spirits, Undead

\emph{Religion}: Spirits, Undead, Celestials

\emph{Dungeon}: Aberrations, Monstrosities, Muds and underground creatures

\emph{Nature}: Beasts, Plants, Faeries

\medskip

The DC of the check is equal to 10 + the creature's Challenge Rating + rarity/notoriety factor (common (0), uncommon (+1), rare (+2), very rare (+4), legendary +(8)).

The information obtainable depends on the margin of success achieved. 

\noindent\begin{itemize}\setlength{\itemsep}{0pt}
\item \emph{within 2}: name, type, main characteristic
\item \emph{up to 7}: which is the best Saving Throw, a resistance/immunity to Conditions, a vulnerability to Conditions, typical attack
\item \emph{up to 12}: which is the worst Saving Throw, a resistance/immunity to Conditions, an immunity to Damage, a vulnerability to Conditions, a vulnerability to a type of Damage
\item \emph{up to 15}: two immunities to Conditions, an immunity to Damage, a vulnerability to Conditions, a vulnerability to a type of Damage
\item \emph{up to 17}: relative challenge rating, i.e. whether it is an easy, medium, high, extraordinary, deadly or epic encounter
\item \emph{up to 20}: special attacks and defences
\end{itemize}

\medskip

The information obtained is cumulative, meaning that if the check succeeds by 15, you get the information within 2, 7 and 12.
\end{dmbox}


\begin{dmbox}[title=Intimidate - page \pageref{intimidate}]
The character uses \textbf{1 Action} and makes an Opposed Check against the Saving Throw on Will with a bonus equal to their Charisma.
If the Saving Throw fails, the opponent has -1 to their Attack Roll against the intimidating character until the end of their next round. The opponent must have an Intelligence equal to or greater than -3. The Saving Throw takes a modifier of $\pm2$ for each difference in size. In case of a critical success, the modifier becomes -2. 

If the person attempting the Intimidate check makes a critical failure, they suffer the same penalties as if they had been intimidated.
\end{dmbox}


\begin{dmbox}[title=Artist of Escape - page \pageref{escapeartist}]
1 Action per 10 DC. 6p 1 Action 15 DC, 12p 1 Action 20 DC.
\end{dmbox}

\begin{dmbox}[title=Stealth - page \pageref{stealth}]
If you want to move silently, the terrain is considered difficult. Moving at full speed while trying not to make noise imposes a 2d6 penalty on Stealth checks.

Using \textbf{1 Action}, you can try to hide from your opponents' view. To hide behind a creature, it must be at least 3 sizes larger than you (otherwise, the creature only provides cover).
\end{dmbox}


\begin{dmbox}[title=Survival - page \pageref{survival}]
Survival can be used in place of \textbf{Disable Devices} with a -1d6 penalty to disable traps or locks. 1 Action per DC.

For every three points gained in the Survival check above 13, the character is able to \textbf{find food} for themselves and one other person, provided they are in an environment capable of sustaining life.
\end{dmbox}

\begin{dmbox}[title=Handle Animals - Tame an animal - page \pageref{handlinganimals}]
is a \textbf{Animal Handling} check with a DC of 12+2*GS of the animal. It takes 1 minute per 3 DC, with 6 points the time is 1 minute per 6 DC, with 12 it is 1 minute per 10 DC to perform the check. The creature must have Intelligence -3 or higher.
\end{dmbox}

\begin{dmbox}[title=Swimming - page \pageref{compnuotare} - \pageref{combatteresottacqua}]
In calm water DC 10, in rough water DC 15, in very rough water DC 20, stormy DC 25. The check is necessary to stay afloat or swim. Swimming in water is considered \textbf{difficult terrain}.
\end{dmbox}

\begin{dmbox}[title=First Aid - page \pageref{firstaid}]
If the character has negative Hit Points, they are dying. The First Aid check, 3 Actions, with a difficulty of 12 plus the value of the negative Hit Points, will bring the character to 0 Hit Points, i.e. unconscious. Each time the character returns to below 0 Hit Points, the difficulty of the First Aid check increases by 2.

A successful check (DC 15) allows you to recover 1d4 Hit Points after a combat or grants a +2 bonus to a Saving Throw against a poison. Must be done within 1 round of the end of combat. Cost: 2 minutes.
With a score of 6, it costs 1 minute and you recover 1d4+4 HP. With a score of 12, it costs 3 rounds and you recover 2d4+8 HP; with a score of 18, it costs 1 round and you recover 3d4+12 HP.

A successful check (base DC 12) reduces \textbf{Bleeding} damage by 1. For each Bleeding value above 1, the difficulty increases by 2. Cost: \textbf{2 Actions}.
A 1-minute treatment guarantees 1 success, no check required. Each successful critical check reduces bleeding by an additional point.

A successful check (base DC 13) to \textbf{care for 8 hours} of a patient restores twice as many Hit Points, with a minimum of 4, and grants a new Saving Throw against Natural Lays or Poisons already in effect.
If performed during rest hours, the person administering the treatment will be Fatigued.
\end{dmbox}

\begin{dmbox}[title=Breaking Objects - DC Strenght]
\begin{tabular}{ll|ll}
Rope & 23&Simple door & 14\\
Good wooden door & 18&Sturdy door & 25\\
Iron door & 30&Chain & 26 \\
\end{tabular}
\end{dmbox}


\begin{dmbox}[title=Breaking Down Doors - page \pageref{tabellaporte}]
\noindent    \resizebox*{!}{0.42\linewidth}{\begin{tabular}{llllll}
\textbf{Door type} & \textbf{Thickness} & \textbf{Strength} & \textbf{HP} & \multicolumn{2}{c}{\textbf{DC}} \\

&\textbf{(cm)}&&& \textbf{Lock} & \textbf{Key}\\
\toprule
Simple wood & 2.5& 5 & 10& 15 & 18\\
Good wood& 3.75 & 5 & 15& 18 & 21\\
Sturdy wood& 5& 5 & 20& 25 & 28\\
Stone& 10 & 8 & 60& 31 & 34\\
Iron & 5& 10& 60& 30 & 33\\
Wooden gate & 7.5& 5 & 30& 27& 30\\
Iron gate & 5& 10& 60& 28& 31\\
Lock& -& 15& 30& -& -\\
Hinges & -& 10& 30& -& -\\
\end{tabular}}
DC vs TS Tempering with Strength modifier
\end{dmbox}




\begin{dmbox}[title=Attack and Defence Modifiers - page \pageref{modifiersattackdefenceparticular}]

\noindent\resizebox*{!}{1\linewidth}{
\begin{tabular}{l|p{3.2cm}|p{3.1cm}}
\multicolumn{2}{c}{\textbf{Attacker}}&\multicolumn{1}{c}{\textbf{Defender}}\\
\textbf{Mod}.&\multicolumn{1}{c}{\emph{Situation}}&\multicolumn{1}{c}{\emph{Situation}}\\
\textbf{-1}& Fatigued (1), Dim light&Fatigued (1)\\
\hline
\textbf{-2}& Fatigued (2), Entangled & Fatigued (2), Grabbed, Entangled, Surprised\\
\hline
\textbf{-4}& Fatigued (3), Prone, Long weapon at close range, non-lethal attack with lethal weapon& Fatigued (3), Prone, Kneeling, Sitting, Restricted, Stunned, Grabbed by a wall, Blocked\\
\hline
\textbf{-1d6}& Restricted, Frightened, Throwing Weapon against melee opponent, Unknown Weapon, Target invisible but Identified, Grabbed by a wall, Blocked&\\
\hline
%\textbf{+1}& & \\
%\hline
\textbf{+2}& Flanking, Elevated Position, Attacking from Behind& Light Cover\\
\hline
\textbf{+4}&& Medium Cover\\
\hline
\textbf{+1d6}& Invisible, Charging, Defenceless Opponent& \\
\hline
\textbf{+8}&& Full Cover
\end{tabular}}

\end{dmbox}


\end{multicols}


\pagebreak

\begin{multicols}{2}


\begin{dmbox}[title=Split - page \pageref{objecthardness}]

\noindent\begin{tabularx}{1\linewidth}{llllX}
\textbf{Material} &\textbf{Durability}&\textbf{HP} & \textbf{DC} & \textbf{Example Items}\\
\toprule{}
Rope, Leather&2&4&19&Hemp rope\\
Thin wood&3&12&14&Chair\\
Leather armour &4&16&22&Leather armour, saddle, thick hemp rope\\
Thin stone&4&16&20&Slate, slate tiles, stone cladding\\
Thin steel or iron&5&20&23&Silk rope, steel shield, short sword\\
Wood&5&20&18&Chest, table\\
Stone&7&28&35&Paving stone, statue\\
Steel or iron&9&36&26&Chain, steel armour, iron, long sword\\
\end{tabularx}\\

The DC refers to a Strength Saving Throw.

\end{dmbox}




\begin{dmbox}[title=Items and Supplies - page \pageref{equipmentlist}]

\noindent\begin{tabular}{ll|ll}
\textbf{Item}&\textbf{Cost}&\textbf{Item}&\textbf{Cost}\\
\hline
&\textbf{Food} &&\\
Banquet (per person)&10 mo&Meat, 1 piece&3 ma\\
Cheese, 1 piece&1 ma&Bread (loaf)&2 mr\\
Travel rations& 3 ma &&\\
\hline
&\textbf{Inn}&&\\
Squalid&7 mr&Poor&1 ma\\
Modest&5 ma&Wealthy&8 ma\\
Rich&2 mo&Aristocratic&4 mo\\
\hline
&\textbf{Meal}&&\\
Squalid&3 mr&Poor&6 mr\\
Modest&3 ma&Wealthy&5 ma\\
Rich&8 ma&Aristocratic&2 mo\\
Good wine (bottle)&10 mo& Ordinary wine (carafe)&2 ma\\
Beer Mug&5 mr&Beer Carafe (4 litres)&2 ma\\
\end{tabular}
\end{dmbox}




\begin{dmbox}[title=Weapons - page \pageref{equipmentweapons}]
\resizebox*{!}{0.94\textheight}{
%\begin{tabularx}{1\linewidth}{lll>{\scriptsize}X}
\begin{tabularx}{1\linewidth}{lll}
\textbf{Weapon}&\textbf{Damage/Damage} & \textbf{Range, List, Special}\\
Halberd& G/1d10 P/T& \textbf{Lances}, \textbf{Poles}, Countercharge, Long weapon, ED9 \\
Composite short bow& M/Arrows& 20 metres, \textbf{Bows}\\
Short bow& M/1d6 P& 15 metres, \textbf{Bows}\\
Composite longbow& G/Arrows& 36 metres, \textbf{Bows}\\
Longbow& G/Arrows& 20 metres, \textbf{Bows}\\
Hammer axe& M/1d6 T/C& \textbf{Axes}\\
One-handed axe& M/1d6 T& 6 metres, \textbf{Axes and Hatchets}, \textbf{Throwing Weapons}, Versatile\\
Battle axe& G/1d10 T&\textbf{Axes and Hatchets}\\
One-handed crossbow& M/Darts& 6 metres, \textbf{Crossbows}\\
Light Crossbow& P/Darts& 15 metres, \textbf{Simple Weapons}, \textbf{Crossbows}\\
Heavy Crossbow& G/Darts& 30 metres, \textbf{Crossbows}\\
Staff& M/1d6 C& \textbf{Simple Weapons}, Long Weapon, Versatile\\
Brandistocco& M/2d4 P/T& \textbf{Lances}, Countercharge, Long weapon\\
Spiked chain& G/2d4 P& 3 metres, \textbf{Spinning balls}, Long weapon\\
Estoc& G/1d8 P& \textbf{Swords}, Long weapon, Parry\\
Scythe& G/2d4 P/T& \textbf{Weapons of Death}, Long weapon\\
Falchion& P/1d6 T& \textbf{Weapons of Death}\\
Poleaxe& G/1d10 P/T& \textbf{Lances}, Countercharge, Long weapon, ED9\\
Falchion& M/2d4 T& \textbf{Graceful Weapons}, ED7\\
Sling& P/1d4 B& 10 metres, \textbf{Throwing Weapons}\\
Double flail& M/1d10 C& \textbf{Spinning Balls}, \textbf{Dual Weapons}\\
Heavy flail& M/1d10 C& \textbf{Spinning balls}\\
Flail& M/1d8 C& \textbf{Spinning balls}, \textbf{Skull crusher}\\
Whip& M/1d3 T& \textbf{Spinning balls}, Long weapon\\
Javelin& P/1d6 P& 12 metres, \textbf{Simple Weapons}, \textbf{Poles}, \textbf{Throwing Weapons}\\
Great double axe& G/1d10 T& \textbf{Axes and Hatchets}, \textbf{Dual Weapons}\\
Large club& M/1d8 C&\textbf{Skull Crusher}\\
Spiked Gauntlet& P/1d4 P&\textbf{Stunning Weapons}\\
Katana& M/1d10 T& \textbf{Lethal Weapons}, ED9\\
Pike& M/1d8 P&3 metres, \textbf{Spears}, Long Weapon, Countercharge\\
Spear& G/1d10 P&\textbf{Spears}, Long weapon, Countercharge\\
Machete& M/1d6 T&\textbf{Lethal weapons}\\
War hammer& G/1d10 C& \textbf{Skull crusher}\\
Truncheon& P/1d6 C& \textbf{Stunning weapons}, non-lethal\\
War hammer& M/1d8 C/P& 6 metres, \textbf{Skull crusher}\\
Light mace& P/1d6 C/T& \textbf{Simple weapons}, \textbf{Light weapons}, \textbf{Skull crusher} \\
Heavy mace& M/1d8 C/T& \textbf{Skull crusher}\\ 
Spiked Club& M 1d8 C/P& \textbf{Simple Weapons}, \textbf{Skull-Shattering}\\
Naginata& G/1d10 T&\textbf{Spears}, Long Weapon, ED9\\
Light Pike& M/1d4 P&\textbf{Weapons of Death}\\
Heavy pike& G/1d6 P&\textbf{Weapons of Death}, Long weapon\\
Dagger& P/1d4 P& 6 metres, \textbf{Simple weapons}, \textbf{Light weapons}, \textbf{Throwing weapons}\\
Fist/Kick & P/1d4 C&Versatile\\
Club& P/1d6 C& \textbf{Simple Weapons}, \textbf{Skull-Splitting Weapons}\\
Scimitar& M/1d6 T&\textbf{Light Weapons}, \textbf{Graceful Weapons}, Versatile\\
Short sword& P/1d6 P&\textbf{Light Weapons}, \textbf{Swords}, Versatile, Parry\\
Longsword& M/1d8 T&\textbf{Swords}, Parry\\
Double-bladed sword& G/1d8 T& \textbf{Dual weapons}, \textbf{Swords}, Parry\\
Bastard sword& M/1d8 T&\textbf{Swords}, Parry, 1d8 one-handed, 2d6 two-handed\\
Broad Sword& M/2d4 T&\textbf{Swords}, Parry, 2d4 one-handed, 1d10 two-handed\\
Two-handed Great Sword& G/2d6 T&\textbf{Swords}, Parry\\
Rapier& P/1d6 P& \textbf{Light Weapons}, \textbf{Graceful Weapons}, Versatile\\
Trident& M/1d6 P/T& 3 metres, \textbf{Poles}, \textbf{Throwing Weapons}, Long Weapon, Countercharge\\
Urgrosh& M/1d6 T/P& \textbf{Lances}, \textbf{Dual Weapons}
\end{tabularx}}
\end{dmbox}


\begin{dmbox}[title=Projectiles - page \pageref{projectiles}]

\begin{tabular}{llll}
\textbf{Projectile Name} & \textbf{Num./MO} & \textbf{Damage/Type} & Weight(kg) \\
Marble balls (slingshots) & 15/1 mo & 1d4 B & 0.2 \\
Light crossbow bolts & 10/1 mo & 1d6 P & 0.1 \\
Heavy crossbow bolts & 3/1 mo & 1d10 P & 0.3 \\
Hunting arrows & 20/1 mo & 1d6 P & 0.1 \\
War arrows & 10/1 mo & 1d8 P & 0.2 \\
Stone (slings) & - & 1d2 B & 0.2 \\
\end{tabular}\\

A \textbf{heavy bolt} for crossbows penetrates metal armour more easily, causing +2 additional damage.

\end{dmbox}


\begin{dmbox}[title=Armour - page \pageref{equipmentarmour}]

\begin{tabular}{llllllll}
\textbf{Armour} & \textbf{Cost} & \textbf{Defence} & \textbf{Penalty} & \textbf{Type} & \textbf{Mov.} & \textbf{Check}&\textbf{Eng.}\\
&(mo)&&\textbf{Comp}.&&&\textbf{Magic}&\\
\hline
Padded 			& 5 gp 		& 1	& 0		& L & 0 & -&2\\
Leather 		& 10 gp 	& 2	& 0 	& L & 0 & +4&2\\
Studded leather	& 25 gp		& 3	& 0 	& L & 0 & +4&2\\
Chain shirt 	& 15 gp 	& 4	& -1 	& M & 0 &+8&4\\
Scale			& 50 gp 	& 5	& -1	& M & 0 &+8&4\\
Ring 			& 150 gp 	& 6	& -1	& M & 0 &+8&4\\
Breastplate		& 200 gp 	& 6	& -2	& M & 0 &+8&4\\
Banded 			& 250 gp 	& 7	& -2	& H & 0 &+16&8\\
Half plate		& 1200 gp	& 8	& -2	& H & 1 &+16&8\\
Field plate		& 1350 gp	& 9	& -3	& H & 2 &+16&8\\
Full plate		& 1500 gp	& 10& -4	& H & 3 &+16&8
\end{tabular}
\end{dmbox}

\begin{dmbox}[title=Shields - page \pageref{shield-table}]
\begin{tabular}{lccccc}
\textbf{Shields} & \textbf{Cost} & \textbf{Defence} & \textbf{Penalty} & \textbf{Check} & \textbf{Encumbrance}\\
&&&\textbf{TC}&\textbf{Magic}&\textbf{Worn}\\
\hline
Light wooden shield & 3 mo & 1& 0& YES & L\\
Light metal shield & 9 mo & 1& 0& YES & L\\
Medium wooden shield &5 mo & 2& 0& +2& M\\
Medium metal shield &12 mo & 2 & 0& +2 & M\\
Heavy wooden shield & 9 mo & 3 & 1& +1.2 & P\\
Heavy metal shield & 20 mo & 3& 1& +1.2 & P\\
\end{tabular}
\end{dmbox}

\begin{dmbox}[title=Magic Check - page \pageref{magieprovadimagia}]
3d6 + Add 1d6 for every 2 Known Magic Lists, ignore one 1 for every 2 Magic Adept versus 10 +2*Spell Level
\end{dmbox}

\begin{dmbox}[title=Distracted - page \pageref{magiedistratto}]
If the caster is severely distracted, hindered, disturbed, bleeding, grabbed, trying to hide the spell, or under attack while trying to cast a spell, they must make a Magic Check.
\end{dmbox}


\begin{dmbox}[title=Magic Points - page \pageref{magiepuntimagia}]

Mod. Characteristic + \\

\noindent\begin{tabularx}{0.45\textwidth}{XX|XX|XX}
\textbf{CM} & \textbf{PM}&\textbf{CM} & \textbf{PM}&\textbf{CM} & \textbf{PM}\\
\hline
\hline
1&	4  &	8&	28&	15&	53\\
2&	7  &	9&	32&	16&	56\\
3&	11 &	10&	35&	17&	60\\
4&	14 &	11&	39&	18&	63\\
5&	18 &	12&	42&	19&	67\\
6&	21 &	13&	46&	20&	70\\
7&	25 & 	14&	49&	20+&	prec.+ 3
\end{tabularx}

\end{dmbox}


\begin{dmbox}[title=Spell Saving Throw - page \pageref{magiesavingthrows}]
DC = 10 + Magic Proficiency + spell-casting ability modifier + 1 x Magic Adept +1 x Critical on Magic Check
\end{dmbox}


\begin{dmbox}[title=Saving Throw for Magic from Objects - page \pageref{saving throws from items}]
DC = 12 + 2 x manifested spell level
\end{dmbox}

\begin{dmbox}[title=Monster Spell Saving Throw - page \pageref{tirosalvezzainccmostro}]
DC is 12 + 2 x spell level + Intelligence or indicated modifier
\end{dmbox}

\begin{dmbox}[title=Auto Magical Critical Success - page \pageref{magienova}]
The spellcaster can decide to spend, in addition to the \textbf{Magic Points} of the spell, an equal amount to automatically gain a \textbf{Magical Critical Success}.

Each time you want to apply an additional Magical Critical Success beyond the first, the Magic Point cost increases by 1. The declaration of intent to use Auto Magical Critical Success must be made before making and passing the Magic Check.

The casting time of a spell enhanced in this way increases by 1 Action.
\end{dmbox}


\begin{dmbox}[title=Reading a Scroll - page \pageref{readscroll}]

\textbf{Isy Scrool}: Understand the spell contained: Intelligence or Arcana DC 10

Cast: Intelligence or Arcane DC 12.

\textbf{Normal scrolls}: Understand: Arcane difficulty 15

Cast: Arcane DC 20 and have access to the Spell List
\end{dmbox}


\begin{dmbox}[title=Follower - page \pageref{magieregoledibase}]
1 Traits shared with Patron. If you are a Follower, you gain +1d6 on Magic Checks in your Patron's preferred school. You can use your Patron's preferred energy in your spells.
\end{dmbox}

\begin{dmbox}[title=Devotee - page \pageref{magieregoledibase}]
2 Traits shared with Patron. A Devotee adds +1d6 to Magic Checks in the Patron's preferred schools and ignores one die rolled on a Magic Check. You must use the Patron's preferred energy in your spells.
\end{dmbox}


\begin{dmbox}[title=Maximum Castable Spell Level - page \pageref{schoolslevels}]
To determine the maximum spell level you can cast, add your Magic Proficiency and Magic Aptitude scores, divide by two, and round up. Compare the result with (twice your spellcasting ability modifier) +1, taking the lower value.
\end{dmbox}

\begin{dmbox}[title=Attempting spells with impediments - page \pageref{magieconimpedimenti}]

x3 Magic Points if unable to gesticulate, x3 if unable to speak; a Magic Check is required in all cases.

Material components within 30 cm of the caster.
\end{dmbox}

\begin{dmbox}[title=Critical Failure on Magic Check - page \pageref{magiccriticalfailureonmagiccheck}]

\textbf{Critical Failure on Magic Check - 3d6 -1d6 x Min. Crit. Failure 1d6}
\begin{tabularx}{1\linewidth}{lX}
1 & For 1 day, you are unable to channel magical energy. You cannot cast spells unless you make a critical magic success on the Magic Check.\\
2 & You increase your Fatigued condition by 2 degrees, up to a maximum of Fatigued 5.\\
3 & You manifest a minor bodily change.\\
4 & You are struck by a booming column of Light and Void. Within a 3-metre radius centred on you, everyone must make a DC 15 Reflex Saving Throw to halve or suffer 1d6 damage for each Magic Point used in the spell\\
5 & For 3 rounds, you are under the influence of the Confusion spell\\
6 & You lose concentration on any spell and speak in rhyme for one minute.\\
7 & You are teleported 3d10 metres in a random direction.\\
8 & You become invisible and paralysed for 6 rounds.\\
9 & Only you are enveloped in a curtain of impenetrable magical darkness for 6 rounds.\\
10 & You cannot speak properly, you are stuttering. Every spell you cast requires you to make a Magic Check. Duration 3 rounds\\
11 & You manifest the spell Anointed under your feet\\
12 & The next spell you cast has its effects minimised if possible\\
13 & Your heartbeat is like the beat of a drum, audible within 36 metres\\
14 & All creatures within 36 metres know exactly where you are and what you were trying to do.\\
15 & All creatures in a 9-metre sphere centred on you take 1d10 Void damage.\\
16 & You gain 2d6 Magic Points\\
17 & An anvil falls, dealing 3d6 damage. Saving Throw on Reflex DC 15 to halve the damage, on a random creature within six metres, excluding you\\
18 & Creatures, excluding you, within 6 metres of you suffer 3d10 unavoidable Strength damage
\end{tabularx}
\end{dmbox}


\begin{dmbox}[title=Alter Magic - page \pageref{altering spells}]
\begin{itemize}[leftmargin=0.5cm,itemsep=-1pt,parsep=0pt]

\item \textbf{Punitive Magic}: a companion paying twice the cost of the spell in Magic Points can allow you to roll an extra die in the Magic Check. This ability can be used up to 3 extra dice per spell. On the part of the companion, it is a Reaction Action to be declared before the Magic Check.

\item \textbf{Effective Magic}: a companion paying three times the spell's cost in Magic Points allows you to ignore one die rolled in the Magic Check. This is a Reaction Action on the part of the companion, to be declared after the Magic Check.

\item \textbf{Ethereal Magic}\index{Ethereal Magic}: by increasing the Magic Points spent on the spell by 3, your spells have full effect on ethereal or incorporeal creatures. Immediate Action to be declared before casting the spell.

\item \textbf{Magical Sacrifice}\index{Magical Sacrifice}: by reducing their Maximum Hit Points by 4, the caster gains 1 Magic Point to be used when casting a spell. You cannot sacrifice more than half of your current Hit Points at a time. Immediate Action.

\item \textbf{Pitiful Magic}\index{Pitiful Magic}: by increasing the Magic Points spent by 3, spells inflict temporary damage.
Spells that inflict damage of a particular type (such as fire) inflict temporary damage of the same type. 1 Action.

\item \textbf{Targeted Magic}\index{Targeted Magic}: For every 2 Magic Points you pay in addition to the spell's cost, you can exclude one person from the spell's area of effect. You cannot exclude more people than the number of times you have taken the Adept of Magic Feat. 1 Action. %1 magic point per spell level per excluded creature

\item \textbf{Far Magic}\index{Far Magic}: By increasing the Magic Points used by 1, you increase the spell's casting range by up to 9 metres. 1 Action.

\item \textbf{Increase casting time}\index{Increase casting time} from 2 Actions to 3 Actions decreases the Magic Points spent on casting the spell by 1, with a minimum cost of 1 Magic Point.

\item \textbf{Circle of Power}\index{Circle of Power}: multiple spellcasters who are all Devotees or Followers of the same Patron can work together to help one of them cast a spell more successfully.
Each caster sacrifices half of the Magic Points of the spell cast by their companion and passes a Magic Check. For every two companions who pass the Magic Check, a critical magic success is generated, up to a maximum of 7 critical magic successes. The casting time of a spell using Circle of Power becomes at least 1 Turn. Prerequisite: Magic Skill 5.

\end{itemize}
\end{dmbox}



\end{multicols}

\end{document}


%\begin{dmbox}[title=Armour wearing times]
%\begin{tabular}{lccc}
%\textbf{Armour type}& \textbf{Wear} & \textbf{in a hurry} & \textbf{Remove}\\
%Shield& 1 action & - & 1 action\\
%Padded, Leather, Reinforced Leather & 1 minute& 3 rounds & - \\
%Chainmail& 1 minute& 5 rounds & 5 rounds\\
%Scales, Rings, Breastplate, Bands & 4 minutes & 1 minute{*} & 1 minute\\
%Half armour, Field, Full & 4 minutes{*}{*}& 4 minutes{*}& 1d4+1 minutes\\
%\end{tabular}\\

%** someone is needed to help put it on
%\end{dmbox}
